---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SummaryTable

The goal of *SummaryTable* is to provide a way to summarize datasets by groups.
It includes a main function, `summarizewith_detail()`, which wraps around `dplyr::group_by()` and `dplyr::summarise()` to compute detailed summary statistics for numeric variables, including the mean, median, standard deviation, maximum, minimum, and range.

## Installation

You can install the development version of SummaryTable like so:

Package installation can be done directly by calling`devtools::install_github("annywm/SummaryTable")`

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SummaryTable)
## basic example code
grade <- data.frame(
subject = rep(c("Math", "English"), each = 3),
score = c(75, 80, NA, 90, 87, 66)
)

summarizewith_detail(grade,subject,score ,2)
```
